---
title: "topic-analysis-reddit"
format: html
---

```{r}
#| output: false 
library(quanteda)
library(tm)
library(topicmodels)
library(topicdoc)   
library(tidyverse)
library(tidytext)
library(reshape2)
library(tictoc)
library(LDAvis)
library(tsne)
library(servr)
```

## Data 
Load Data 
Data from: https://academictorrents.com/details/1614740ac8c94505e4ecb9d88be8bed7b6afddd4 
Data is subreddit comments filtered for environmental, zero_waste, and european from 2005-06 to 2024-12. 

```{r}
data_path <- "~/Documents/MEDS/eds231_text_analysis/sentimentAnalysis-EU2021_PlasticBans/data/reddit/subreddits24"

env <- stream_in(file(file.path(data_path, "environment_filtered.ndjson")))
zer <- stream_in(file(file.path(data_path, "ZeroWaste_filtered.ndjson")))
eur <- stream_in(file(file.path(data_path, "european_filtered.ndjson")))

all_comments <- bind_rows(env, zer)
```


## Build & Clean **Corpus**

Build the corpus
```{r}
#| warning: false 
#| output: false 
tbl <- all_comments
corpus <- corpus(x = tbl, 
                 text_field = "body")
```

Tokenize and clean 
```{r}
# Stop words 
add_stops <- c(quanteda::stopwords("en", 
                                   source="smart"),
               # remove other meta data words 
               "said", "says", "told", "according", "discuss", "because", "where", "vol", "pg", "newstex")


# Tokenize 
toks <- tokens(corpus, 
               remove_punct = TRUE, 
               remove_numbers = TRUE, 
               remove_symbols = TRUE) %>% 
  # Normalize
  tokens_tolower() 

# Remove stop words 
toks1 <- tokens_select(toks, pattern = add_stops, selection = "remove")
```

## Build the Document-Feature Matrix

```{r}
# Creating a dfms
dfm1 <- dfm(toks1) 
dfm2 <- dfm_trim(dfm1, 
                 min_docfreq = 5,  # Reduce by limiting min values of feature's doc frequency
                 min_termfreq = 10) # appears at least 10 times total

# Remove empty rows b/c LDA will error on these
sel_idx <- slam::row_sums(dfm2) > 0 # select no empty rows 
dfm <- dfm2[sel_idx,] # subset
```

## Select K uysing Multiple Critiera 

Initialize Model (Theory-Driven k)
```{r}
# Define Hyperparameter 
k <- 3

# Model 
topicModel_k3 <- LDA(dfm, # matrix
                      k, 
                      method = "Gibbs", # Gibbs is default (always do this)
                      control = list(iter = 100, # Number of iterations
                                     verbose = 25, # Tell us after every 25 iterations
                                     seed = 321
                                     ))

```


Evaluate 
```{r}
result <- posterior(topicModel_k3)

beta  <- result$terms
theta <- result$topcis

cat("phi dimensions  (topics × vocab):", dim(beta), "\n")

# Top 10 terms per topic
terms(topicModel_k3, 10)
```

## Selecting k with Coherence Scores
```{r}
# Fit model for a range of k values
k_values <- seq(2, 15, by = 1) 

tic() # Timerstart


# Increase iterations
coherence_results <- map_dfr(k_values, function(k){
  # Run the model 
  m <- LDA(dfm, k = k, 
      method = "Gibbs", 
      control = list(iter = 1000,   # was 300
                     burnin = 200,  # discard first 200 iterations
                     seed = 231,
                     verbose = 0))
   # Calculate coherence 
  coh <- mean(topic_coherence(m, dfm))
  tibble(k = k, coherence = coh)
})

toc() # Timer end 
```

Plotting coherence VS K
```{r}
ggplot(coherence_results, aes(x = k, y = coherence)) +
  geom_line(color = "darkorchid4") +
  geom_point(color = "darkorchid4", size = 2) +
  geom_vline(xintercept = coherence_results$k[which.max(coherence_results$coherence)], # Best coh score 
             linetype = "dashed", color = "violetred2") +
  labs(title = "Mean topic coherence by number of topics (k)",
       subtitle = "Dashed line = k with highest coherence",
       x = "Number of topics (k)",
       y = "Mean coherence score") +
  theme_minimal()
```


## Fit the Selected Model 
```{r}
k <- 3  # update this based on your coherence plot

topicModel_k_select <- LDA(dfm, k,
                           method = "Gibbs",
                           control = list(iter = 1000, # Increasing the quality of model result 
                                          verbose = 25,
                                          seed = 321))

tmResult <- posterior(topicModel_k_select)
terms(topicModel_k_select, 10)

theta <- tmResult$topics
beta  <- tmResult$terms
vocab <- colnames(beta)
```

```{r top_terms_plot}
topics <- tidy(topicModel_k_select, matrix = "beta")

top_terms <- topics |>
  group_by(topic) |>
  slice_max(beta, n = 10) |>
  ungroup() |>
  arrange(topic, -beta)

top_terms |>
  mutate(term = reorder_within(term, beta, topic, sep = "")) |>
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free_y") +
  scale_x_reordered() +
  coord_flip() +
  labs(title = "Top 10 terms per topic",
       subtitle = "β = P(term | topic)",
       x = NULL, y = "β") +
  theme_minimal()
```