---
title: "sentiment-analysis-Readit"
format: html
---


```{r}
library(atrrr)
library(tidyverse)
library(tidytext)
library(sentimentr)
library(remotes)
library(textdata)
library(jsonlite)
library(dplyr)
library(lubridate)
```


## Data 
Load Data 
Data from: https://academictorrents.com/details/1614740ac8c94505e4ecb9d88be8bed7b6afddd4 
Data is subreddit comments filtered for environmental, zero_waste, and european from 2005-06 to 2024-12. 

```{r}
data_path <- "~/Documents/MEDS/eds231_text_analysis/sentimentAnalysis-EU2021_PlasticBans/data/reddit/subreddits24"

env <- stream_in(file(file.path(data_path, "environment_filtered.ndjson")))
zer <- stream_in(file(file.path(data_path, "ZeroWaste_filtered.ndjson")))
eur <- stream_in(file(file.path(data_path, "european_filtered.ndjson")))

all_comments <- bind_rows(env, zer)
```


# Clean and Prepare Text 
```{r}
# filter for neccessary columns 
all_comments <- all_comments[,1:17]

all_comments <- all_comments %>%
  mutate(
    #date  = as.Date(date),
    text_clean = str_remove_all(body, "https?\\S+"), # remove URLs
    text_clean = str_remove_all(text_clean, "@\\S+"),# remove mentions
    text_clean = str_replace_all(text_clean, "\u2019", "'"), # normalize all curly ' to R's '
    text_clean = str_remove_all(text_clean, "'s\\b"), # remove possessives
    text_clean = str_remove_all(text_clean, "[0-9]+$"), # remove numbers 
    text_clean = str_squish(text_clean), # cleans all the added white space 
    date = as_datetime(as.numeric(created_utc))
  ) %>%
  filter(nchar(text_clean) > 10) %>% 
  filter(date >= as.Date("2021-07-01")) %>%  # filter for >2021 
  filter(str_detect(body, regex("EU|european union|SUP directive|single.use plastic directive|brussels", # Filter for ~ EU SUP BAN
                                ignore_case = TRUE)))

all_comments

```

Number of articles 
```{r}
nrow(all_comments)
```

# Word Frequency 

Remove Stop words 
```{r}
# Standard stop words
data("stop_words")

tokens_clean <- all_comments |>
  unnest_tokens(word, text_clean) |>
  anti_join(stop_words, by = "word")

# Custom stop words 
custom_sw <- tibble(word = c(
  # search terms
  "fig", "says", "vol"
))

tokens_clean2 <- tokens_clean %>%
  anti_join(custom_sw, by = "word")

```

Look at the post frequent words 
```{r}
word_counts <- tokens_clean2 %>% 
  count(word, sort = TRUE)

word_counts %>%
  slice_max(n, n =20) %>% 
  ggplot(aes(x = reorder(word, n), y = n)) + 
  geom_col(fill = "#6c91c9") + 
  coord_flip() + 
  labs(
    title = "Top 20 words in Readit posts about SUPs", 
    x = "Words", 
    y = "count") + 
  theme_minimal()
```

# Sentiment Analysis 

## Bing Lexicon 

The Bing lexicon is a polarity / binary lexicon grouping where yes/no = positive/negative on a word-level. It is a list of words and their positive or negative sentiments.

```{r}
# Load lexicon 
bing_lexicon <- get_sentiments("bing")

# Score posts with Bing
bing_scores <- all_comments %>% 
  # Tokenize posts 
  unnest_tokens(word, text_clean) %>% 
  # Join the words to the sentiment lexicon 
  inner_join(bing_lexicon, by = "word") %>% 
  count(id, sentiment) %>% 
  pivot_wider(names_from = sentiment, 
              values_from = n, 
              values_fill = 0) %>% 
  # Calculate total sentiment score: positives - negative 
  mutate(score_b = positive - negative) 

# Join scores to posts  
all_comments <- all_comments %>%
  left_join(bing_scores, "id") %>% 
  mutate(bing_score = replace_na(score_b, 0)) %>%  # NA scores = 0 
  select(-c(score_b))

# Check if it joined the score column 
colnames(all_comments)

```

Graph 
```{r}
bing_scores %>% 
  ggplot() + 
  geom_histogram(aes(score_b), fill = "orange") + 
  geom_vline(aes(xintercept = 0)) + 
  theme_light() + 
  labs(title = "Bing Scores", 
       x = "Score", 
       y = "Count")
```


## AFINN Lexicon 
```{r}
# Load AFINN 
afinn <- get_sentiments("afinn")

# Score text
afinn_scores <- all_comments %>%
  # Tokenize posts 
  unnest_tokens(word, text_clean) %>% 
  # Inner Join the words to the sentiment lexicon  
  inner_join(afinn, by = "word") %>% 
  # Score: sum of afinn scores for each URI 
  group_by(id) %>% 
  summarise(score_af = sum(value), .groups = "drop")

# Join scores to posts  
all_comments <- all_comments %>% 
  left_join(afinn_scores, "id") %>% 
  mutate(afinn_score = replace_na(score_af, 0)) %>% # NA scores = 0 
  select(-c(score_af))

```

Graph 
```{r}
afinn_scores %>% 
  ggplot() + 
  geom_histogram(aes(score_af), fill = "#69b269") + 
  geom_vline(aes(xintercept = 0)) + 
  theme_light() + 
  labs(title = "AFINN Scores", 
       x = "Score", 
       y = "Count")
```
Create a time series plot that shows bing and affin scores overtime 
```{r}
# Make sure date is in Date format
all_comments <- all_comments %>%
  mutate(date = as.Date(date))

# Time series plot
ggplot(all_comments, aes(x = date)) +
  # Plots 
  geom_smooth(aes(y = bing_score, color = "Bing"), method = "loess", se = TRUE) +
  geom_smooth(aes(y = afinn_score, color = "AFINN"), method = "loess", se = TRUE) +
  # Line
  geom_vline(xintercept = as.Date("2021-07-03"), linetype = "dashed", color = "red") +
  annotate("text", x = as.Date("2021-07-03"), y = max(all_comments$afinn_score, na.rm=TRUE), 
           label = "SUP Directive\nTakes Effect", hjust = -0.1, size = 3, color = "red") +
  # Style 
  scale_color_manual(values = c("Bing" = "orange", 
                                "AFINN" = "darkgreen")) +
  labs(title = "Media Sentiment Toward EU Single-Use Plastics Policy Over Time",
       x = "Date", y = "Normalized Sentiment Score", color = "Lexicon") +
  theme_minimal()
```


## NRC lexicon 
```{r}
# Load NRC 
nrc <- get_sentiments("nrc")

# Score text - Count emotion words per post
nrc_scores <- all_comments %>% 
  # Tokenized posts 
  unnest_tokens(word, text_clean) %>% 
  # Join to NRC 
  inner_join(nrc, by = "word", relationship = "many-to-many") %>% 
  # Count emotion words per post 
  group_by(id, sentiment) %>% 
  summarise(nrc_count = n(), .groups = "drop") 

#Join to post
all_comments <- all_comments %>%
  left_join(nrc_scores, by = "id") %>% 
  rename(nrc_sentiment_words = sentiment)
```

Graphs 
```{r}
# ----- Top emotions in corpus ----- 
nrc_scores %>%
  group_by(sentiment) %>%
  summarise(nrc_count = sum(nrc_count), .groups = 'drop') %>%
  ggplot() +
  geom_col(aes(y = reorder(sentiment, nrc_count), x = nrc_count), 
           fill = "#458cb2") +
  theme_light() +
  labs(title = "Emotion Words in NRC Search", x = "Count", y = "Sentiment Words")

# ----- What words are driving each emotion? ----- 
# Find frequency of words for each sentiment 
sentiment_word_count <- all_comments %>% 
  unnest_tokens(word, text_clean) %>% # Tokenized posts
  inner_join(nrc, by = "word", relationship = "many-to-many") %>% # Join to NRC 
  count(sentiment, word, sort = TRUE)  # Count of words per sentiment 

# Get the top 10 most frequent words for each sentiment group 
top_10 <- sentiment_word_count %>% 
  group_by(sentiment) %>% 
  slice_max(order_by = n, n = 10, with_ties = FALSE) %>%
  ungroup()

# Plot the top 10 words for each sentiment group 
ggplot(top_10, aes(x = reorder_within(word, n, sentiment), y = n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  scale_x_reordered() +  # Keeps ordering within facets
  facet_wrap(~ sentiment, scales = "free_y") +
  labs(
    title = "Top 10 Words per Sentiment Group",
    x = "Word",
    y = "Frequency"
  ) +
  coord_flip() + 
  theme_minimal()

```

## sentimentr

```{r}
sr_scores <- sentiment_by(all_comments$text_clean) %>%
  select(element_id, ave_sentiment) %>%
  rename(sr_score = ave_sentiment) %>%
  mutate(element_id = as.integer(element_id))

# Join sr score back into posts by row index 
all_comments <- all_comments %>%
  mutate(element_id = row_number()) %>%
  left_join(sr_scores, by = "element_id") %>% 
  select(-c(element_id))
```

```{r}
sr_scores %>% 
  ggplot() + 
  geom_histogram(aes(sr_score), fill = "#c14545") + 
  geom_vline(aes(xintercept = 0)) + 
  theme_light() + 
  labs(title = "Sentimentr Scores", 
       x = "Score", 
       y = "Count")

sr_scores
```

## VADER 

```{r}
all_comments <- all_comments %>% 
  mutate(vader_score = purrr::map_dbl(text_clean, ~ tidyvader::vader_chr(.x)$compound))
```

```{r}
# purple
all_comments %>% 
  group_by(id) %>% 
  summarise(vader_score = mean(vader_score)) %>% 
  ggplot() + 
  geom_histogram(aes(vader_score), fill = "#954aa5") +
  geom_vline(aes(xintercept = 0)) + 
  labs(
    title = "VADER score", 
    x = "Score", 
    y = "Count") +
  theme_light()
```

##  Compare 

**Correlation**
```{r}
all_comments %>% 
  select(bing_score, afinn_score, sr_score, vader_score) %>% # Select 4 scores 
  cor(use = "complete.obs") 
```
**Score distributions**
```{r}
all_comments %>% 
  pivot_longer(cols = c(bing_score, afinn_score, sr_score, vader_score), 
               names_to = "method", 
               values_to = "scores") %>% 
  ggplot() + 
  geom_histogram(aes(scores, fill = method), show.legend = FALSE) + 
  facet_wrap(~method) + 
  theme_bw()
```
**Misclassifications**
```{r}
all_comments %>% 
  select(c(text_clean, bing_score, vader_score)) %>% 
  # New column with score signs 
  mutate(bing_flag = sign(bing_score),
         #afinn_flag = sign(afinn_score),
         #sr_flag = sign(sr_score),
         vadar_flag = sign(vader_score)
         ) %>% 
  # Filter for posts where two methods point in opposite directions 
  # Picking bing and VADAR 
  filter((bing_flag == -1 & vadar_flag == 1) | 
         (bing_flag == 1 & vadar_flag == -1))



all_comments %>% 
  # Text per row and keep only neccessary columns  
  select(c(text_clean, bing_score, vader_score)) %>% 
  group_by(text_clean) %>% 
  summarise(bing_score = mean(bing_score), 
            vader_score = mean(vader_score)) %>% 
  # New column with score signs 
  mutate(bing_flag = sign(bing_score),
         #afinn_flag = sign(afinn_score),
         #sr_flag = sign(sr_score),
         vadar_flag = sign(vader_score)
         ) %>% 
  # Filter for posts where two methods point in opposite directions 
  # Picking bing and VADAR 
  filter((bing_flag == -1 & vadar_flag == 1) | 
         (bing_flag == 1 & vadar_flag == -1)) %>% 
  # Compute the absolute difference between the two scores 
  mutate(abs_difference = abs(bing_score) - abs(vader_score)) %>% 
  # Arrange for highest-conflict first 
  arrange(desc(abs_difference))
```

